A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
NM

\paragraph{Contributions}
The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). In this work, erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}. As seen in the figure, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which, evaluated on solid boundaries, reduces to shear. In this way, vorticity provides a convenient tool for visualizing local erosion rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
In this fashion, individual pores are resolved rather than
homogenized.  A boundary integral equation (BIE) is used to solve the
incompressible Stokes equations in the complex geometry.  The resulting
method resolves individual grains and the non-negligible interactions
between bodies.  To link the eroding body and fluid dynamics, the body
is eroded in the normal direction at a rate that is proportional to the
magnitude of the shear stress.

>>>>

\paragraph{Contributions}
The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}. As seen in the figure, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vsp{2}
The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
In this fashion, individual pores are resolved rather than
homogenized.  A boundary integral equation (BIE) is used to solve the
incompressible Stokes equations in the complex geometry.  The resulting
method resolves individual grains and the non-negligible interactions
between bodies.  To link the eroding body and fluid dynamics, the body
is eroded in the normal direction at a rate that is proportional to the
magnitude of the shear stress.
